Quantum Pseudo-Telepathy

### 2023-06-24 paper/main.tex
Proof for intersection

\section{Quantum Unitaries (? research)}
\label{sec:quantum-unitaries}

>>>>

Lemma~\ref{lem:product} shows that the quantum solution satisfies the
requirements of the game for every row and column. Now, we move on to
show that Alice and Bob always agree in the value that they assign
to the intersection of the row and column.

\begin{lemma}[The Intersection Property of the Quantum Solution]
  \label{lem:intersection}
  For any row \(i\) assigned to Alice and column \(j\) assigned to
  Bob, the value ascribed to the cell \((i, j)\) by Alice and Bob,
  after they have performed their measurements, is always the same.
\end{lemma}

\begin{proof}
  To prove that Alice and Bob agree at the intersection, it suffices
  to look to the eigenvectors shared by each set of mutually commuting
  operators, shown in Tables~\ref{tab:eigenv-rows} and
  \ref{tab:eigenv-cols}.  Notice that, regardless of the row assigned
  to Alice, the state of her subsystem after her measurements is
  always one of the eigenvectors in that row. This state is always a
  linear combination of one of Bob's eigenspaces for the cell in the
  intersection (the same applies if we consider first Bob than Alice).
  Take, for instance, the second row and first column. Suppose that
  Alice's measurements collapsed her qubits to
  \((\nicefrac{1}{2}) (\ket{00} - \ket{01} - \ket{10} + \ket{11})\).
  This state can be written as
  \((\nicefrac{1}{\sqrt{2}}) (\ket{00} - \ket{10}) -
  (\nicefrac{1}{\sqrt{2}}) (\ket{01} - \ket{11})\), a linear
  combination of the \(-1\)-eigenspace depicted in
  Table~\ref{tab:eigenv-cols} (column 1, row 2).  What is left is to
  show that Bob's state will be exactly the same as Alice's, implying
  that Bob shall observe the same result. This follows from the fact
  that the initial state is already symmetric (the first qubit of
  Alice is equal to the first qubit of Bob; the same is true for their
  second qubits) and the symmetry is preserved by any measurement
  performed by Alice and Bob. For the first row, it is easy to see.
  The others are trickier, but it all boils down to doing the
  calculations.  Consider, for instance, the second row, and suppose
  that the outcomes were \(-1\), \(-1\) and \(+1\), so that Alice's
  state collapsed to
  \((\nicefrac{1}{2}) (\ket{00} - \ket{01} - \ket{10} +
  \ket{11})\). The state after the first measurement is
  \begin{align}
    &\frac{1}{2\sqrt{2}} \Bigl(
    (\ket{00} - \ket{10}) \ket{00} +
    (\ket{01} - \ket{11}) \ket{01} +
    (\ket{10} - \ket{00}) \ket{10} +
    (\ket{11} - \ket{01}) \ket{11}
    \Bigr) \nonumber \\
    \equiv\;
    & \frac{1}{2\sqrt{2}} \Bigl(
      \ket{00} (\ket{00} - \ket{10}) +
      \ket{01} (\ket{01} - \ket{11}) +
      \ket{10} (\ket{10} - \ket{00}) +
      \ket{11} (\ket{11} - \ket{01})
    \Bigr).
  \end{align}
  And, the state after the three measurements is
  \begin{alignat}{2}
    &\frac{1}{4} \Bigl(
      &&(\ket{00} - \ket{01} - \ket{10} + \ket{11}) \ket{00} -
        (\ket{00} - \ket{01} - \ket{10} + \ket{11}) \ket{01} - \nonumber \\
    & &&(\ket{00} - \ket{01} - \ket{10} + \ket{11}) \ket{10} +
      (\ket{00} - \ket{01} - \ket{10} + \ket{11}) \ket{11}
    \Bigr) \nonumber \\
    \equiv\;
    & \frac{1}{4} \Bigl(
      &&\ket{00} (\ket{00} - \ket{01} - \ket{10} + \ket{11}) -
        \ket{01} (\ket{00} - \ket{01} - \ket{10} + \ket{11}) - \nonumber \\
    & &&\ket{10} (\ket{00} - \ket{01} - \ket{10} + \ket{11}) +
        \ket{11} (\ket{00} - \ket{01} - \ket{10} + \ket{11})
    \Bigr).
  \end{alignat}
  The calculations for the other rows and columns are similar, so we omitted them.
  \qed
\end{proof}
\section{Quantum Unitaries (? research)}
\label{sec:quantum-unitaries}
